Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-07-07 paper_jasa.tex
comment on p-value difference

In the previous section we noticed that subjects tend to pick the plot with the lowest $p$-value. If a null plot has data that, by chance because the sample is a random draw from the null, has a smaller $p$-value than the actual data, we would expect that there is a strong possibility that an subject will pick this null plot instead of the actual data plot. Figure \ref{fig:pval_difference} investigates this for the data collected in experiments 1 and 2. The plots display the proportion of subjects who choose the actual data plot against the $p$-value of the actual data minus the lowest seen in the null data. A small negative value of the difference means that the $p$-value of the actual data is smaller than that of the null data. If there is a big negative difference we'd expect to see that the subjects would more often make the correct choice of plot. When there is a large positive difference, subjects fail to pick the correct plot. If however, there is little difference between the $p$-values then we'd expect to see more confusion in the choices. That is why we see a big range of proportion correct where difference is close to zero in Figure \ref{fig:pval_difference}.

>>>>

\blue{In the previous section we noticed that subjects tend to pick the plot with the lowest $p$-value. If a null plot has data that, by chance because the sample is a random draw from the null, has a smaller $p$-value than the actual data, we would expect that there is a strong possibility that an subject will pick this null plot instead of the actual data plot. Figure \ref{fig:pval_difference} investigates this for the data collected in experiments 1 and 2. The plots display the proportion of subjects who choose the actual data plot against the $p$-value of the actual data minus the lowest seen in the null data. A small negative value of the difference means that the $p$-value of the actual data is smaller than that of the null data. If there is a big negative difference we'd expect to see that the subjects would more often make the correct choice of plot. When there is a large positive difference, subjects fail to pick the correct plot. If however, there is little difference between the $p$-values then we'd expect to see more confusion in the choices. That is why we see a big range of proportion correct where difference is close to zero in Figure \ref{fig:pval_difference}.}
